Supplement to `\ourlongtitle'

### 2021-10-13 Final_version/glo-2020-prel.tex
Added final version

We first introduce some general notation. 
For any $m, n \in \zset$ such that $m \leq n$, we let $\intvect{m}{n}$ denote the set $\{m, \ldots, n\}$. For arbitrary elements $a_\ell$, $\ell \in \intvect{m}{n}$, we denote vectors by $a_{m:n} = (a_m, \ldots, a_n)$. The sets of measures, probability measures, and real-valued bounded measurable functions on some given state-space $(\mathsf{X}, \mathcal{X})$ are denoted by $\meas{\mathcal{X}}$, $\probmeas{\mathcal{X}}$, and $\bmf{\mathcal{X}}$, respectively. For any measure $\mu$ and measurable function $h$ we let $\mu h \eqdef \int h(x) \, \mu(\rmd x)$ denote the Lebesgue integral of $h$ with respect to $\mu$ whenever this is well defined. When $h$ depends on several variables we may write $\mu[h(\cdot,y)]\eqdef \int h(x,y) \, \mu(\rmd x)$ to avoid any confusion. We will write $\mu^2 f = (\mu f)^2$ (whereas $\mu f^2 = \mu(f^2)$). For any finite set $S$, $\powerset{S}$ denotes the power set of $S$. The following kernel notation will be used repeatedly in the paper. Let $(\mathsf{X}, \mathcal{X})$ and $(\mathsf{Y}, \mathcal{Y})$ be general state spaces and $\kernel{K} : \mathsf{X} \times \mathcal{Y} \to \rsetnn$ some transition kernel. Then $\kernel{K}$ induces two operators, one acting on measurable functions and the other on measures. More precisely, for any $h \in \bmf{\mathcal{X} \tensprod \mathcal{Y}}$ and $\mu \in \meas{\mathcal{X}}$, let 
$$
\kernel{K} h : \mathsf{X} \ni x \mapsto \int h(x, y) \, \kernel{K}(x, \rmd y), \quad \mu \kernel{K} : \mathcal{Y} \ni A \mapsto \int \mu(\rmd x) \, \kernel{K}(x, A)
$$ 
Moreover, let $(\mathsf{Z}, \mathcal{Z})$ be a third state space and $\kernel{K}' : \mathsf{Y} \times \mathcal{Z} \to \rsetnn$ another kernel; then the product of $\kernel{K}$ and $\kernel{K}'$ is the kernel defined by 
$$
\kernel{K} \kernel{K}' : (x, A) \ni \mathsf{X} \times \mathcal{Z} \mapsto \int \kernel{K}(x, \rmd y) \, \kernel{K}'(y, A). 
$$

@@

With notations as in Section~\ref{sec:introduction}, define, for each $n \in \nset$ and $m \in \intvect{0}{n}$, the kernel 
\begin{equation} \label{eq:def:uk:products}
    \uk{m, n}(x_{0:m}', \rmd x_{0:n + 1}) \eqdef \delta_{x_{0:m}'}(\rmd x_{0:m}) \prod_{\ell = m}^n \uk{\ell}(x_\ell, \rmd x_{\ell + 1}) 
\end{equation}
on $\Xset^m \times \Xfd^{n + 1}$. In addition, let $\uk{n, n - 1} = \operatorname{id}$. Note that $\uk{n, n}$ is different from $\uk{n}$ in the sense that the former is defined on $\Xset^n \times \Xfd^{n + 1}$ whereas the latter is defined on $\Xset_n \times \Xfd_{n + 1}$. We will always assume that for all $n \in \nset$, $\chi \uk{0, n - 1} \1_{\Xset^n} = \chi \uk{0} \cdots \uk{n - 1} \1_{\Xset_n} > 0$. Since each mapping $\uk{m, n} \1_{\Xset^n}$ depends only on the last coordinate $x_m$, a version of this mapping with domain $\Xset_m$ is well defined; we will denote the latter by the same symbol and write $\uk{m, n} \1_{\Xset^n}(x_m)$, $x_m \in \Xset_m$, when needed. Using the previous notations, the path measures \eqref{eq:def:post} can be expressed as 
\begin{equation}
\label{eq:FK:path}
    \post{0:n}(\rmd x_{0:n}) = \frac{\chi \uk{0, n - 1}(\rmd x_{0:n})}{\chi \uk{0, n - 1} \1_{\Xset^n}}, \quad n \in \nset. 
\end{equation} 
For each $n \in \nset$, let  
$ 
\post{n} : A \ni \Xfd_n \mapsto \post{0:n}(\Xset^{n - 1} \times A)
$
denote the marginal of $\post{0:n}$ with respect to the last component. In the case of state-space models, see Example~\ref{ex:state-space:models}, $\post{0:n}$ is usually referred to as the joint smoothing distribution and $\post{n}$ as the filtering distribution. Note that the path- and marginal-measure flows can be expressed recursively as  
\begin{equation} \label{eq:recursion:FK:path}
    \post{0:n + 1}(\rmd x_{0:n + 1}) = \frac{\post{0:n} \uk{n, n}(\rmd x_{0:n + 1})}{\post{0:n} \uk{n, n} \1_{\Xset^{n + 1}}} = \frac{\post{0:n} \uk{n, n}(\rmd x_{0:n + 1})}{\post{n} \uk{n} \1_{\Xset_{n + 1}}}, \quad n \in \nset, 
\end{equation}
and 
\begin{equation} \label{eq:recursion:FK:marg}
    \post{n + 1}(\rmd x_{n + 1}) = \frac{\post{n} \uk{n}(\rmd x_{n + 1})}{\post{n} \uk{n} \1_{\Xset_{n + 1}}}, \quad n \in \nset, 
\end{equation}
respectively. Given some sequence $(\addf{n})_{n \in \nset}$ of functions $\addf{n} : \Xset_n \times \Xset_{n + 1} \to \rset$, our aim is, as declared in Section~\ref{sec:introduction}, the online approximation of $(\post{0:n} h_n)_{n \in \nset}$, where $h_n$ defined by \eqref{eq:add:func}.

@@

\begin{example}[state-space models]
\label{ex:state-space:models}
Let $(\Xset, \Xfd)$ and $(\Yset, \Yfd)$ be general state spaces and $(\hk_n)_{n \in \nset}$ and $(\mk_n)_{n \in \nset}$ sequences of Markov kernels on $\Xset \times \Xfd$ and $\Xset^2 \times \Yfd$, respectively. In addition, let $\chi$ be some probability measure on $\Xfd$. Consider a fully dominated model where all $\mk_n$ and $\hk_n$ have transition densities $\md{n}$ and $\hd{n}$ with respect to some reference measures $\nu$ and $\mu$ on $\Yfd$ and $\Xfd$, respectively. Let $\{X_0, (X_n, Y_n) : n \in \nsetpos\}$ be the canonical Markov chain induced by the initial distribution $\chi$ and the Markov transition kernel $\hk_n(x_n, \rmd x_{n + 1}) \, \mk_n(x_n, x_{n + 1}, \rmd y_{n + 1})$ (which has no dependence on the $y_n$ variable; the same dynamics hence applies to the first transition $X_0 \rightsquigarrow (X_1, Y_1)$) and denote by $\pP_\chi$ its law with corresponding expectation $\pE_\chi$. In this model, we assume that the \emph{state process} $(X_n)_{n \in \nset}$ is latent and only partially observed thought the \emph{observation process} $(Y_n)_{n \in \nsetpos}$. It can be shown that (i) the state process is itself a Markov chain with initial distribution $\chi$ and transition kernels $(\hk_n)_{n \in \nset}$ and (ii) conditionally on the state process, the observations are independent and such that the marginal distribution of $Y_n$ is given by $\mk_{n - 1}(X_{n - 1}, X_n, \cdot)$ for all $n$. In the case where $\mk_{n - 1}$ does not depend on $x_{n - 1}$, the model is a fully adapted general state-space HMM; see \cite[Section~2.2]{Cappe:2005:IHM:1088883}. In this setting, the joint-smoothing distribution at time $n \in \nset$ is, for a given record $y_{1:n} \in \Yset^n$ of observations, defined as the probability measure  
\begin{equation}
\label{eq:smooth}
    \post{0:n} \langle y_{1:n} \rangle (\rmd x_{0:n}) \eqdef \llh{n}^{-1}(y_{1:n}) \chi(\rmd x_0) \prod_{m = 0}^{n - 1} \hk_m(x_m, \rmd x_{m + 1}) \, \md{m}(x_m, x_{m + 1}, y_{m + 1}), 
\end{equation}
on $\Xfd^n$, where   
\begin{equation}
    \label{eq:likelihood}
    \llh{n}(y_{1:n}) \eqdef \idotsint \chi(\rmd x_0) \prod_{m = 0}^{n - 1} \hk_m(x_m, \rmd x_{m + 1}) \, \md{m}(x_m, x_{m + 1}; y_{m + 1})
\end{equation}
is the observed data likelihood. Along the lines of \cite[Proposition~3.1.4]{Cappe:2005:IHM:1088883} one may show that $\post{0:n} \langle Y_{1:n} \rangle$ is, $\pP_\chi$-a.s., the conditional distribution of $X_{0:n}$ given $Y_{1:n}$. The marginal  $\post{n} \langle y_{1:n} \rangle$ of the joint smoothing distribution with respect to its last component $x_n$ is referred to as the \emph{filtering distribution at time $n$}. Consequently, by defining kernel densities $\ud{n}(x_n, x_{n + 1}) \eqdef \md{n}(x_n, x_{n + 1}, y_{n + 1}) \hd{n}(x_n, x_{n + 1})$ for all $n \in \nset$ (while keeping dependence on observations implicit) and letting $\uk{n}$ be the induced transition kernels, the joint-smoothing distributions may be expressed in the form \eqref{eq:FK:path}.
\end{example}

@@

Assume for a moment that each transition density $\ud{n}$ is available in a closed form. Then standard SMC methods (see \cite{chopin:papaspiliopoulos:2020} for a recent introduction) can be used to approximate the distribution flows $(\post{0:n})_{n \in \nset}$ and $(\post{n})_{n \in \nset}$ using Monte Carlo samples generated recursively by means of sequential importance sampling and resampling operations. In order to set notations, let us recall the most general class of such algorithms, the so-called auxiliary particle filters \cite{pitt:shephard:1999}. In the light of Remark~\ref{we:vs:delmoral} it is enough to consider particle approximation of the marginals $(\post{n})_{n \in \nset}$. We proceed recursively and assume that we, at time $n \in \nset$, have at hand a sample $(\epart{n}{i}, \ewght{n}{i})_{i = 1}^\N$ of $\Xset_n$-valued \emph{particles} (the $\epart{n}{i}$) and associated nonnegative importance weights (the $\ewght{n}{i}$) such that the self-normalised estimator $\post[\N]{n} h \eqdef \sumwght{n}^{-1} \sum_{i = 1}^\N \ewght{n}{i} h(\epart{n}{i})$, with $\sumwght{n} \eqdef \sum_{i = 1}^\N \ewght{n}{i}$, approximates $\post{n} h$ for every $\post{n}$-integrable function $h$. Then plugging $\post[\N]{n}$ into the recursion \eqref{eq:recursion:FK:marg} yields the approximation $\sum_{i = 1}^\N \pi_n(i, \rmd x)$ of $\post{n + 1}$, where 
\begin{equation} \label{eq:def:partmixt}
\partmixt_n(i, \rmd x) \propto \ewght{n}{i} \uk{n}(\epart{n}{i}, \rmd x)
\end{equation}
is a mixture distribution on $\powerset{\intvect{1}{\N}} \tensprod \Xfd_{n + 1}$. In order to form new particles approximating $\post{n + 1}$, we may draw, using importance sampling, pairs $(\ind{n + 1}{i}, \epart{n + 1}{i})_{i = 1}^\N$ of indices and particles from $\partmixt_n$ and discard the former. For this purpose, we introduce some instrumental mixture distribution 
\begin{equation} \label{eq:cond:instrumental:mixture}
\rho_n(i, \rmd x) \propto \ewght{n}{i} \adjfuncforward{n}(\epart{n}{i}) \, \prop{n}(\epart{n}{i}, \rmd x)
\end{equation}
on the same space, where $\adjfuncforward{n}$ is a real-valued positive \emph{adjustment-weight function} on $\Xset_n$ and $\prop{n}$ is a proposal kernel on $\Xset_n \times \Xfd_{n + 1}$ such that $\uk{n}(x, \cdot) \ll \prop{n}(x, \cdot)$ for all $x \in \Xset_n$. Adjustment multiplier weights were introduced in \cite{pitt:shephard:1999} to propose data-driven proposal distributions and design robust filtering estimates. These weights usually depend on the new observation and are often chosen to approximate the predictive likelihood of the new observation given the current particle. For further discussions see for instance \cite[Chapter~8]{Cappe:2005:IHM:1088883}.

We will always assume that $\prop{n}$ has a transition density $\propdens{n}$ with respect to $\mu_{n + 1}$. A draw $(\ind{n + 1}{i}, \epart{n + 1}{i})$ from $\rho_n$ is easily generated by first drawing $\ind{n + 1}{i}$ from the categorical distribution induced by the adjusted importance weights and then drawing $\epart{n + 1}{i}$ by randomly moving the selected ancestor $\epart{n}{{\ind{n + 1}{i}}}$ according to the proposal kernel. These steps are often referred to as \emph{selection} and \emph{mutation}, respectively. 
Finally, each draw $\epart{n + 1}{i}$ is assigned the updated importance weight $\ewght{n + 1}{i}$ proportional to $\rmd \partmixt_n / \rmd \rho_n (\ind{n + 1}{i}, \epart{n + 1}{i})$, and the estimator $\post[\N]{n + 1} h = \sumwght{n + 1}^{-1} \sum_{i = 1}^\N \ewght{n + 1}{i} h(\epart{n + 1}{i})$ approximates $\post{n + 1} h$ for every $\post{n + 1}$-integrable $h$. The full update, which we will refer to as \emph{forward sampling} and express in a short form as
\begin{equation} \label{eq:forward:sampling}
    (\epart{n + 1}{i}, \ewght{n + 1}{i})_{i = 1}^\N \sim \mathsf{FS}((\epart{n}{i}, \ewght{n}{i})_{i = 1}^\N),   
\end{equation}
is summarised in Algorithm~\ref{alg:ideal:SMC}.\footnote{Mathematically, the forward sampling operation defines a Markov transition kernel, which motivates the use of the symbol $\sim$ in \eqref{eq:forward:sampling}.}

@@

Finally, we note that the re-weighting operation on Line~4 in Algorithm~\ref{alg:ideal:SMC} requires the transition density $\ud{n}$ to be tractable, which is not the case in general. We will return to the general case in Section~\ref{sec:pseudo:marginal:PaRIS}.

@@

%The following quantities will play a key role in the following. 
For each $m \in \nset$, define the  \emph{backward Markov kernel} 
\begin{equation} \label{eq:def:backward:kernel}
    \bkw{m}(x_{m + 1}, \rmd x_m) \eqdef \frac{\post{m}(\rmd x_m) \, \ud{m}(x_m, x_{m + 1})}{\post{m}[\ud{m}(\cdot, x_{m + 1})]}
\end{equation}
on $\Xset_{m + 1} \times \Xfd_m$. In addition, for each $n \in \nsetpos$, let the Markov kernel   
\begin{equation} \label{eq:def:tstat}
\tstat{n}(x_n, \rmd x_{0:n - 1}) \eqdef \prod_{m = 0}^{n - 1} \bkw{m}(x_{m + 1}, \rmd x_m)
\end{equation}
on $\Xset_n \times \Xfd^{n - 1}$ denote the joint law of the backward Markov chain induced by the kernels \eqref{eq:def:backward:kernel} when initialised at $x_n \in \Xset_n$. An important class of sequential Monte Carlo joint-smoothing methods \cite{doucet2000sequential,godsill:doucet:west:2004} is based on the following result. 
\begin{lemma} 
\label{lem:reversibility}
\

>>>>

We first introduce some general notation. 
For any $(m, n) \in \zset^2$ such that $m \leq n$, we let $\intvect{m}{n}$ denote the set $\{m, \ldots, n\}$. For arbitrary elements $a_\ell$, $\ell \in \intvect{m}{n}$, we denote vectors by $a_{m:n} = (a_m, \ldots, a_n)$. The sets of measures, probability measures, and real-valued bounded measurable functions on some given state-space $(\mathsf{X}, \mathcal{X})$ are denoted by $\meas{\mathcal{X}}$, $\probmeas{\mathcal{X}}$, and $\bmf{\mathcal{X}}$, respectively. For any measure $\mu$ and measurable function $h$ we let $\mu h \eqdef \int h(x) \, \mu(\rmd x)$ denote the Lebesgue integral of $h$ with respect to $\mu$ whenever this is well defined. When $h$ depends on several variables we may write $\mu[h(\cdot,y)]\eqdef \int h(x,y) \, \mu(\rmd x)$ to avoid any confusion. We will write $\mu^2 f = (\mu f)^2$ (whereas $\mu f^2 = \mu(f^2)$). For any finite set $S$, $\powerset{S}$ denotes the power set of $S$. The following kernel notation will be used repeatedly in the paper. Let $(\mathsf{X}, \mathcal{X})$ and $(\mathsf{Y}, \mathcal{Y})$ be general state spaces and $\kernel{K} : \mathsf{X} \times \mathcal{Y} \to \rsetnn$ some transition kernel. Then $\kernel{K}$ induces two operators, one acting on measurable functions and the other on measures. More precisely, for any $h \in \bmf{\mathcal{X} \tensprod \mathcal{Y}}$ and $\mu \in \meas{\mathcal{X}}$, let 
$$
\kernel{K} h : \mathsf{X} \ni x \mapsto \int h(x, y) \, \kernel{K}(x, \rmd y), \quad \mu \kernel{K} : \mathcal{Y} \ni A \mapsto \int \mu(\rmd x) \, \kernel{K}(x, A). 
$$ 
Moreover, let $(\mathsf{Z}, \mathcal{Z})$ be a third state space and $\kernel{K}' : \mathsf{Y} \times \mathcal{Z} \to \rsetnn$ another kernel; then the product of $\kernel{K}$ and $\kernel{K}'$ is the kernel defined by 
$$
\kernel{K} \kernel{K}' : (x, A) \ni \mathsf{X} \times \mathcal{Z} \mapsto \int \kernel{K}(x, \rmd y) \, \kernel{K}'(y, A). 
$$

@@

With notations as in Section~\ref{sec:introduction}, define, for each $n \in \nset$ and $m \in \intvect{0}{n}$, the kernel 
\begin{equation} \label{eq:def:uk:products}
    \uk{m, n}(x_{0:m}', \rmd x_{0:n + 1}) \eqdef \delta_{x_{0:m}'}(\rmd x_{0:m}) \prod_{\ell = m}^n \uk{\ell}(x_\ell, \rmd x_{\ell + 1}) 
\end{equation}
on $\Xset^m \times \Xfd^{n + 1}$. In addition, let $\uk{n, n - 1} = \operatorname{id}$. Note that $\uk{n, n}$ is different from $\uk{n}$ in the sense that the former is defined on $\Xset^n \times \Xfd^{n + 1}$ whereas the latter is defined on $\Xset_n \times \Xfd_{n + 1}$. We will always assume that for all $n \in \nset$, $\chi \uk{0, n - 1} \1_{\Xset^n} = \chi \uk{0} \cdots \uk{n - 1} \1_{\Xset_n} > 0$. Since each mapping $\uk{m, n} \1_{\Xset^n}$ depends only on the last coordinate $x_m$, a version of this mapping with domain $\Xset_m$ is well defined; we will denote the latter by the same symbol and write $\uk{m, n} \1_{\Xset^n}(x_m)$, $x_m \in \Xset_m$, when needed. Using the previous notations, the path measures \eqref{eq:def:post} can be expressed as 
\begin{equation}
\label{eq:FK:path}
    \post{0:n}(\rmd x_{0:n}) = \frac{\chi \uk{0, n - 1}(\rmd x_{0:n})}{\chi \uk{0, n - 1} \1_{\Xset^n}}, \quad n \in \nset. 
\end{equation} 
For each $n \in \nset$, let  
$ 
\post{n} : A \ni \Xfd_n \mapsto \post{0:n}(\Xset^{n - 1} \times A)
$
denote the marginal of $\post{0:n}$ with respect to the last component. In the case of state-space models, $\post{0:n}$ and $\post{n}$ are usually referred to as the \emph{joint-smoothing} and \emph{filter distribution at time $n$}, respectively; see Example~\ref{ex:state-space:models} for details. Note that the path- and marginal-measure flows can be expressed recursively as  
\begin{equation} \label{eq:recursion:FK:path}
    \post{0:n + 1}(\rmd x_{0:n + 1}) = \frac{\post{0:n} \uk{n, n}(\rmd x_{0:n + 1})}{\post{0:n} \uk{n, n} \1_{\Xset^{n + 1}}} = \frac{\post{0:n} \uk{n, n}(\rmd x_{0:n + 1})}{\post{n} \uk{n} \1_{\Xset_{n + 1}}}, \quad n \in \nset, 
\end{equation}
and 
\begin{equation} \label{eq:recursion:FK:marg}
    \post{n + 1}(\rmd x_{n + 1}) = \frac{\post{n} \uk{n}(\rmd x_{n + 1})}{\post{n} \uk{n} \1_{\Xset_{n + 1}}}, \quad n \in \nset, 
\end{equation}
respectively. Given some sequence $(\addf{n})_{n \in \nset}$ of functions $\addf{n} : \Xset_n \times \Xset_{n + 1} \to \rset$, our aim is, as declared in Section~\ref{sec:introduction}, the online approximation of $(\post{0:n} h_n)_{n \in \nset}$, where $h_n$ defined by \eqref{eq:add:func}.

@@

\begin{example}[state-space models]
\label{ex:state-space:models}
Let $(\Xset, \Xfd)$ and $(\Yset, \Yfd)$ be general state spaces and $(\hk_n)_{n \in \nset}$ and $(\mk_n)_{n \in \nset}$ sequences of Markov kernels on $\Xset \times \Xfd$ and $\Xset^2 \times \Yfd$, respectively. In addition, let $\chi$ be some probability measure on $\Xfd$. Consider a fully dominated model where all $\mk_n$ and $\hk_n$ have transition densities $\md{n}$ and $\hd{n}$ with respect to some reference measures $\nu$ and $\mu$ on $\Yfd$ and $\Xfd$, respectively. Let $\{X_0, (X_n, Y_n) : n \in \nsetpos\}$ be the canonical Markov chain induced by the initial distribution $\chi$ and the Markov transition kernel $\hk_n(x_n, \rmd x_{n + 1}) \, \mk_n(x_n, x_{n + 1}, \rmd y_{n + 1})$ (which has no dependence on the $y_n$ variable; the same dynamics hence applies to the first transition $X_0 \rightsquigarrow (X_1, Y_1)$) and denote by $\pP_\chi$ its law with corresponding expectation $\pE_\chi$. In this model, we assume that the \emph{state process} $(X_n)_{n \in \nset}$ is latent and only partially observed thought the \emph{observation process} $(Y_n)_{n \in \nsetpos}$. It can be shown that (i) the state process is itself a Markov chain with initial distribution $\chi$ and transition kernels $(\hk_n)_{n \in \nset}$ and (ii) conditionally on the state process, the observations are independent and such that the marginal distribution of $Y_n$ is given by $\mk_{n - 1}(X_{n - 1}, X_n, \cdot)$ for all $n$. In the case where $\mk_{n - 1}$ does not depend on $x_{n - 1}$, the model is a fully adapted general state-space HMM; see \cite[Section~2.2]{Cappe:2005:IHM:1088883}. In this setting, the joint-smoothing distribution at time $n \in \nset$ is, for a given record $y_{1:n} \in \Yset^n$ of observations, defined as the probability measure  
\begin{equation}
\label{eq:smooth}
    \post{0:n} \langle y_{1:n} \rangle (\rmd x_{0:n}) \eqdef \llh{n}^{-1}(y_{1:n}) \chi(\rmd x_0) \prod_{m = 0}^{n - 1} \hk_m(x_m, \rmd x_{m + 1}) \, \md{m}(x_m, x_{m + 1}, y_{m + 1}), 
\end{equation}
on $\Xfd^n$, where   
\begin{equation}
    \label{eq:likelihood}
    \llh{n}(y_{1:n}) \eqdef \idotsint \chi(\rmd x_0) \prod_{m = 0}^{n - 1} \hk_m(x_m, \rmd x_{m + 1}) \, \md{m}(x_m, x_{m + 1}; y_{m + 1})
\end{equation}
is the observed data likelihood. Along the lines of \cite[Proposition~3.1.4]{Cappe:2005:IHM:1088883} one may show that $\post{0:n} \langle Y_{1:n} \rangle$ is, $\pP_\chi$-a.s., the conditional distribution of $X_{0:n}$ given $Y_{1:n}$. The marginal  $\post{n} \langle y_{1:n} \rangle$ of the joint smoothing distribution with respect to its last component $x_n$ is referred to as the filtering distribution at time $n$. Consequently, by defining kernel densities $\ud{n}(x_n, x_{n + 1}) \eqdef \md{n}(x_n, x_{n + 1}, y_{n + 1}) \hd{n}(x_n, x_{n + 1})$ for all $n \in \nset$ (while keeping dependence on observations implicit) and letting $\uk{n}$ be the induced transition kernels, the joint-smoothing distributions may be expressed in the form \eqref{eq:FK:path}.
\end{example}

@@

Assume for a moment that each transition density $\ud{n}$ is available in a closed form. Then standard SMC methods (see \cite{chopin:papaspiliopoulos:2020} for a recent introduction) can be used to approximate the distribution flows $(\post{0:n})_{n \in \nset}$ and $(\post{n})_{n \in \nset}$ using Monte Carlo samples generated recursively by means of sequential importance sampling and resampling operations. In order to set notations, let us recall the most general class of such algorithms, the so-called auxiliary particle filters \cite{pitt:shephard:1999}. In the light of Remark~\ref{we:vs:delmoral} it is enough to consider particle approximation of the marginals $(\post{n})_{n \in \nset}$. We proceed recursively and assume that we, at time $n \in \nset$, have at hand a sample $(\epart{n}{i}, \ewght{n}{i})_{i = 1}^\N$ of $\Xset_n$-valued \emph{particles} (the $\epart{n}{i}$) and associated nonnegative importance weights (the $\ewght{n}{i}$) such that the self-normalised estimator $\post[\N]{n} h \eqdef \sumwght{n}^{-1} \sum_{i = 1}^\N \ewght{n}{i} h(\epart{n}{i})$, with $\sumwght{n} \eqdef \sum_{i = 1}^\N \ewght{n}{i}$, approximates $\post{n} h$ for every $\post{n}$-integrable function $h$. Then plugging $\post[\N]{n}$ into the recursion \eqref{eq:recursion:FK:marg} yields the approximation $\sum_{i = 1}^\N \pi_n(i, \rmd x)$ of $\post{n + 1}$, where 
\begin{equation} \label{eq:def:partmixt}
\partmixt_n(i, \rmd x) \propto \ewght{n}{i} \uk{n}(\epart{n}{i}, \rmd x)
\end{equation}
is a mixture probability distribution on $\powerset{\intvect{1}{\N}} \tensprod \Xfd_{n + 1}$. In order to form new particles approximating $\post{n + 1}$, we may draw, using importance sampling, pairs $(\ind{n + 1}{i}, \epart{n + 1}{i})_{i = 1}^\N$ of indices and particles from $\partmixt_n$ and discard the former. For this purpose, we introduce some instrumental mixture distribution 
\begin{equation} \label{eq:cond:instrumental:mixture}
\rho_n(i, \rmd x) \propto \ewght{n}{i} \adjfuncforward{n}(\epart{n}{i}) \, \prop{n}(\epart{n}{i}, \rmd x)
\end{equation}
on the same space, where $\adjfuncforward{n}$ is a real-valued positive \emph{adjustment-weight function} on $\Xset_n$ and $\prop{n}$ is a proposal kernel on $\Xset_n \times \Xfd_{n + 1}$ such that $\uk{n}(x, \cdot) \ll \prop{n}(x, \cdot)$ for all $x \in \Xset_n$. 
Adjustment multiplier weights were introduced in \cite{pitt:shephard:1999} with the aim to robustify particle filtering estimates in nonlinear state-space HMMs using data-driven proposal distributions. In \cite{cornebise:moulines:olsson:2008} it is shown that the adjustment-weight function minimising the Kullback--Leibler divergence between $\partmixt_n$ and $\rho_n$ is, for any $\prop{n}$, given by the---typically intractable---mapping $x \mapsto \uk{n}(x, \Xset_{n + 1})$; thus, $\adjfuncforward{n}$ should be chosen as some approximation of this function, which in the HMM context coincides with the predictive likelihood of the state at time $n$ given the new observation $y_{n + 1}$. We will always assume that $\prop{n}$ has a transition density $\propdens{n}$ with respect to $\mu_{n + 1}$. A draw $(\ind{n + 1}{i}, \epart{n + 1}{i})$ from $\rho_n$ is easily generated by first drawing $\ind{n + 1}{i}$ from the categorical distribution induced by the adjusted importance weights and then drawing $\epart{n + 1}{i}$ by randomly moving the selected ancestor $\epart{n}{{\ind{n + 1}{i}}}$ according to the proposal kernel. These steps are often referred to as \emph{selection} and \emph{mutation}, respectively. Finally, each draw $\epart{n + 1}{i}$ is assigned the updated importance weight $\ewght{n + 1}{i}$ proportional to $\rmd \partmixt_n / \rmd \rho_n (\ind{n + 1}{i}, \epart{n + 1}{i})$, and the estimator $\post[\N]{n + 1} h = \sumwght{n + 1}^{-1} \sum_{i = 1}^\N \ewght{n + 1}{i} h(\epart{n + 1}{i})$ approximates $\post{n + 1} h$ for every $\post{n + 1}$-integrable $h$. The full update, which we will refer to as \emph{forward sampling} and express in a short form as
\begin{equation} \label{eq:forward:sampling}
    (\epart{n + 1}{i}, \ewght{n + 1}{i})_{i = 1}^\N \sim \mathsf{FS}((\epart{n}{i}, \ewght{n}{i})_{i = 1}^\N),   
\end{equation}
is summarised in Algorithm~\ref{alg:ideal:SMC}.\footnote{Mathematically, the forward sampling operation defines a Markov transition kernel, which motivates the use of the symbol $\sim$ in \eqref{eq:forward:sampling}.}

@@

Finally, we note that the re-weighting operation on Line~4 in Algorithm~\ref{alg:ideal:SMC} requires the transition density $\ud{n}$ to be tractable, which is, as mentioned, not the case in general. We will return to the general case in Section~\ref{sec:pseudo:marginal:PaRIS}.

@@

For each $m \in \nset$, define the  \emph{backward Markov kernel} 
\begin{equation} \label{eq:def:backward:kernel}
    \bkw{m}(x_{m + 1}, \rmd x_m) \eqdef \frac{\post{m}(\rmd x_m) \, \ud{m}(x_m, x_{m + 1})}{\post{m}[\ud{m}(\cdot, x_{m + 1})]}
\end{equation}
on $\Xset_{m + 1} \times \Xfd_m$. In addition, for each $n \in \nsetpos$, let the Markov kernel   
\begin{equation} \label{eq:def:tstat}
\tstat{n}(x_n, \rmd x_{0:n - 1}) \eqdef \prod_{m = 0}^{n - 1} \bkw{m}(x_{m + 1}, \rmd x_m)
\end{equation}
on $\Xset_n \times \Xfd^{n - 1}$ denote the joint law of the backward Markov chain induced by the kernels \eqref{eq:def:backward:kernel} when initialised at $x_n \in \Xset_n$. An important class of sequential Monte Carlo joint-smoothing methods \cite{doucet2000sequential,godsill:doucet:west:2004} is based on the following result. 
\begin{lemma} 
\label{lem:reversibility}
\
